%-------------------------
% Resume in Latex
% Author : Lloyd Mason
% Based off of: https://github.com/lloydmason/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage[sfdefault]{carlito}

% \usepackage[T1]{fontenc}
% \usepackage{fix-cm}

\usepackage[sfdefault,lf]{carlito}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \texttt{Lloyd Mason}} \\ \vspace{1pt}
    \small +45 41663369 $|$ \href{mailto:lloyd1@live.dk}{\underline{lloyd1@live.dk}} $|$ 
    \href{https://linkedin.coProven track m/in/lloyd-mason}{\underline{linkedin.com/in/lloyd-mason}} $|$
    \href{https://github.com/lloydmason95}{\underline{github.com/lloydmason95}}
\end{center}

%-----------EDUCATION-  ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Aarhus University}{Aarhus, DK}
      {Master of Science in Business Intelligence (MSc)}{Aug 2018 -- May 2020}
    \resumeSubheading
      {Aarhus University}{Aarhus, DK}
      {Bachelor in Business Administration (HA Almen, BSc)}{Aug 2015 -- May 2018}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Platform Engineer, Freelance}{Aug 2022 -- Present }
      {Banking Circle, FinTech}{Copenhagen, DK}
      \resumeItemListStart
        \resumeItem{Designed and implemented a cloud platform powering an event-driven, service-oriented architecture utilizing Azure Service Bus and Event Hubs, with workloads distributed across Kubernetes, App Services, and Virtual Machines.}
        \resumeItem{Implemented and tested high availability and failover mechanisms across critical Azure services—including workloads on AKS, App Services, and VMs running in active/active across regions, as well as SQL Servers, Storage Accounts, Key Vaults, and Azure Service Bus—utilizing geo-replication and zone redundancy to ensure business continuity and increase performance.}
        \resumeItem{Streamlined code delivery of .NET applications by building CI/CD pipelines that automated testing, coverage validation, and rapid builds, while enabling reliable infrastructure releases through IaC and other scripting.}
        \resumeItem{Designed and implemented a network architecture aligned with business-critical application flows, using Azure VNets, Subnets, NSGs, and Private Endpoints to enhance security for the banks mission-critical components.}
        \resumeItem{Built a IaC solution delivering infrastructure across 20+ repositories to support microservices, enhancing transparency, developer productivity, and codebase consistency.}
        \resumeItem{Acted as a central enabler between teams supporting platform infrastructure, Kubernetes operations, cloud governance, and stakeholder alignment across the platform landscape.}        
        \resumeItem{Collaborated with the CCoE to deliver a suite of standardized, test-driven Terraform modules, enabling self-service infrastructure provisioning for development teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Cloud Solution Architect, Freelance}{Aug 2024 -- Present}
      {Mindcore}{Copenhagen, DK}
      \resumeItemListStart
        \resumeItem{Advisory on and implementation of Azure Landing Zones based on Enterprise-Scale architecture and CAF principles, tailored on the customers cloud maturity focusing on workloads, identity, security, and governance.}
        \resumeItem{Implemented containerization using Docker and Kubernetes to modernize legacy applications, streamline deployment, and improve scalability and resource efficiency.}
        \resumeItem{Conducted cost analysis and optimization in Azure, focusing on reservation strategies, workload rightsizing, and improving overall cost efficiency.}
        \resumeItem{Developed strategic cloud transformation roadmaps covering migration, modernization, and platform alignment.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineer, Cloud Engineer, Full-time}{Oct 2020 -- Jul 2022}
      {Inspari}{Copenhagen, DK}
      \resumeItemListStart
        \resumeItem{Delivered end-to-end data platform solutions for SMBs and enterprise clients, leveraging Azure Databricks, Data Factory, and Synapse Analytics to streamline data integration and model ETL workflows.}
        \resumeItem{Conducted hypercare activities, including monitoring data volume, job executions, sql query performance, and system cleanup to ensure platform stability and performance.}
        \resumeItem{Recognized as Employee of the Year by management, leadership, and peers for outstanding contributions and team collaboration.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Certifications}{: Azure Solutions Architect Expert, Azure Administrator (AZ-104), Designing MS Azure Infrastructure Solutions (AZ-305), and Azure Administrator Associate.\\
        \textbf{Languages}{: Python, SQL, R, HCL (Terraform), YAML, JSON, Bicep, PowerShell, Bash} \\
        \textbf{Frameworks}{: .NET, Java} \\
        \textbf{Developer Tools}{: Git, Docker, Kubernetes, Helm, Terraform, Linux} \\
        \textbf{CI/CD}{: ArgoCD, Azure DevOps, GitHub Actions} \\
        \textbf{Clouds}{: Microsoft Azure, Amazon Web Services (AWS)} \\
        \textbf{Soft Skills}{: Clear Communication, cross-team collaboration, analytical problem solving, strategic thinking, Adaptability}}}}        
 \end{itemize}


%-------------------------------------------
\end{document}
